\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-03-03 manuscript/manuscript.tex
smoothed intro

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ be that $X_i$'s follow the
hypothesized distribution~$F$.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}

The KS statistic 
can be used to see if a population follows a hypothesized distribution and can 
be applied to a variety of fields. It has
been used to analyze the random distribution of cosmic microwave background 
radiation \citep{naess2012application}. \citet{zeimbekakis2022misuses} reviews
some of the common misuses of the one-sample KS test. One of the most common 
misuses of the KS test is when
the hypothesized distribution has unspecified parameters. 
\citet{babu2004goodness} approaches this scenario using basic 
non-parametric bootstrap. There is also the scenario where the data are serially
dependent, which \citet{zeimbekakis2022misuses} partially remedies with 
semi-parametric
bootstrap. The last scenario \citet{zeimbekakis2022misuses} discusses is that
where both the hypothesized 
distribution has unspecified parameters and the data are 
serially dependent. \citet{zeimbekakis2022misuses}'s remedy for
this scenario also uses semi-parametric bootstrap.

A non-parametric remedy for KS tests with serially dependent data is
a challenging task. The null distribution depends on the structure of the serial
dependence, which can be arbitrary in practice. A parametric bootstrap procedure
would demand a specification for a model for the dependence, whereas the primary 
interest
is to test the marginal distribution of the stationary series. A bias 
correction
for block bootstrap similar to what \citet{babu2004goodness} did for basic
bootstrap had not yet been shown.  This study aims to resolve this gap by 
demonstrating a bias 
correction
for non-parametric block bootstrap to use when the hypothesized distribution
has unspecified parameters and the data are serially dependent.

The rest of the paper is outlined as follows: Section~\ref{sec:methods} reviews
block bootstrap procedure and demonstrates the basis for bias correction for
the non-parametric block bootstrap KS test. In Section~\ref{sec:simu}, we first 
assess whether the KS
test holds its size; that is, does the test fail to reject the null hypothesis
when it is true. In the second part of Section~\ref{sec:simu}, we 
evaluate the 
test's power; that is, does the test reject the null hypothesis when it is 
false. We show practical applications of this method in Section~\ref{sec:real}.
First, we apply the method to test if annual maximums of hourly precipitation
in three U.S. airports follows the GEV distribution in 
Subsection~\ref{sec:precipitation}.
Then, we test if Microsoft stock return data follows the Normal or the Student's
$t$ distribution in Subsection~\ref{sec:microsoft}.
Finally, we end with 
concluding remarks in Section~\ref{sec:conclusion}.

@@

@@

\bibliographystyle{chicago}
\bibliography{citations}

>>>>

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ be that $X_i$'s follow the
hypothesized distribution~$F$.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}
As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. The distribution function can be
accurately evaluated in modern statistical software
\citep{marsaglia2003evaluating}. The KS test can be applied to a variety of
fields. \jy{cite a few  references in various field to show its wide
  applications.}
 It has
been used to analyze the random distribution of cosmic microwave background 
radiation \citep{naess2012application}.

Despite its widespread use, the Kolmogorov-Smirnov (KS) test can be 
misapplied when its foundational assumptions are overlooked. The KS test 
assumes the data are independently and identically distributed (i.i.d.) and 
that the hypothesized distribution is continuous and fully specified without 
the need for parameter estimation. \citet{zeimbekakis2022misuses} examines 
common misapplications of the one-sample KS test, notably the inappropriate
use when the hypothesized distribution contains unspecified parameters.
Another commonly encountered situation is when the data are serially
dependent. \citet{babu2004goodness} addresses this issue through the
application of basic non-parametric bootstrap methods. Alternatively, 
\citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
where the serial dependence structure is modeled via a working serial copula.
A particularly complex scenario arises when the distribution has unspecified
parameters, and the data are serially dependent. For this,
\citet{zeimbekakis2022misuses} also recommends a semi-parametric bootstrap
approach, where the parameters of the hypothesized distribution and the serial
dependence both need to be estimated and their uncertainty accounted for.

Developing a fully non-parametric solution for the Kolmogorov-Smirnov (KS) 
tests in the presence of serially dependent data presents a significant 
challenge. The null distribution's characteristics are intricately linked to 
the structure of the serial dependence, which can vary widely in practical 
situations. Employing a parametric bootstrap would necessitate defining a 
specific model for this dependence, despite the primary focus being on 
evaluating the marginal distribution of a stationary series. To date, a bias 
correction method for block bootstrap, akin to the approach \citet{babu2004goodness} 
applied to the basic bootstrap, has not been established. This study seeks 
to bridge this gap by introducing a bias correction technique for the 
non-parametric block bootstrap, tailored for use in scenarios where the 
hypothesized distribution includes unspecified parameters and the data 
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent.

The remainder of this paper is structured as follows: 
Section~\ref{sec:methods} provides an overview of the block bootstrap 
procedure and introduces the bias correction methodology for the 
non-parametric block bootstrap KS test. Section~\ref{sec:simu} is divided 
into two parts; initially, we evaluate the KS test's ability to maintain 
its size, i.e., its consistency in not rejecting the null hypothesis when 
it is indeed true. Subsequently, we examine the test's power, assessing 
whether it can reject the null hypothesis when it is false. Practical 
applications of our method are presented in Section~\ref{sec:real}, where 
we first apply the approach to assess whether annual maximums of hourly 
precipitation at three U.S. airports conform to the Generalized Extreme 
Value (GEV) distribution in Subsection~\ref{sec:precipitation}. Following 
this, we analyze if Microsoft stock return data adhere to either the Normal 
or the Student's $t$ distribution in Subsection~\ref{sec:microsoft}. The 
paper concludes with Section~\ref{sec:conclusion}, offering final thoughts 
and remarks.

@@

\jy{The number of references seems low. Need to cite more related works.}

@@

\bibliographystyle{asa}
\bibliography{citations}
